Constant Error Tolerance Computational Fuzzy Extractors

### 2014-02-04 trunk/constantRate/ConstCompFuzzExt.tex
edited E.1 and E.2, working on E.3

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}

@@

\subsection{Obfuscation}
Our construction uses obfuscation for a family of point function $\mathcal{I} = \{I_w\}_{w \in \zo^*}$ defined as follows:
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
\]
The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}. This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}) as it allows the simulator to run in unbounded time while making at most polynomial number of oracle queries to the function. In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input. Compassable auxiliary-input VGB obfuscators for point function are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Difﬁe Hellman assumption which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.

\begin{definition}[$t$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
\label{def:obf} Let $\mathcal{I}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is a $t$-composable VGB obfuscator for $\mathcal{I}$ with auxiliary-input if the following conditions are met:
\begin{enumerate}
\item \emph{Functionality:} for every $I \in \mathcal{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^t \in \mathcal{I}_n$, (where $t=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
\[
|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^t)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^t)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^t|}) = 1] | < \frac{1}{p(n)} \enspace,
\]
where $(I^1,\dots,I^t)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
\end{enumerate}
\end{definition}

@@

\begin{definition}
\label{def:block guessable}
Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that returns \[\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=
\begin{cases}
1 & w_i = w_i'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.
We discuss  block unguessable distributions in \apref{sec:characterize}.  \consref{cons:first construction} is secure for block unguessable distributions:
\begin{theorem}
\label{thm:security of cons}
Let $\mathcal{O}$ be an $\ell$-composable virtual gray box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.  Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{theorem}

@@

Combining the last two sections, we have that \consref{cons:sampling} is secure and correct:
\begin{theorem}
Let $n$ be a security parameter.
Let $\mathcal{W}$ be the family of $(\alpha = \omega(1), \beta\leq \gamma(1/2-\Theta(1)))$-unordered block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.  Let $\eta = \omega(\log n)$ and $\ell = O(\poly(n)) = \omega(\log n)$.  Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.  Then for $s_{sec} = \poly(n)$ there exists some $\epsilon = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ for
\begin{align*}
t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} \\
\tilde{m} &=|C|\\
\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
\end{align*}
\end{theorem}

\subsection{Discussion of \consref{cons:sampling}}
\consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.  The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.  We are able to correct $O(\gamma/\eta)$ errors.
This yields:
\begin{align*}
gap &= \Hoo(W) -\log |B_t| \\
&< \Theta(\gamma)- t \log |\mathcal{Z}|\\
&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|\\
\end{align*}
That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.  If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.  However, in this setting $gap =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
\bibliographystyle{alpha}
\bibliography{crypto}

\appendix
\section{Obfuscation}
\label{sec:obfuscation}
The standard notion of obfuscation is virtual black-box obfuscation~(introduced by Barak et al.~\cite{barak2001possibility}).  This notion is known to be impossible in a black-box way for all polynomial time programs.  Several variants~(best possible obfuscation~\cite{goldwasser2007best}, indistinguishability obfuscation~\cite{barak2001possibility}, differing inputs indistinguishability obfuscation~\cite{barak2001possibility}) have been presented~(see Varia~\cite{varia2010studies} for implications between various definitions).  Indistinguishability obfuscation has recently been shown to be constructible~\cite{garg2013candidate} using multilinear maps~\cite{garg2013multilinear}.  The definition of virtual black box obfuscation is presented in \defref{def:obf}.

In this work, we will use obfuscation of point-programs,
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}
\]

We present the construction of Canetti~\cite{canetti1997towards}, as an illustration of how point functions can be obfuscated.  Let $G$ be a group:
\begin{enumerate}
\item Input: string $w\in \zo^n$.
\item Choose a generator $g\overset{\$}\leftarrow G$
\item Compute $h\leftarrow g^w$, where $w$ is viewed as an element of $G$ is some canonical way.
\item Output: circuit that has $g, h$ hardwired, and on input $x$, accepts iff $g^x=h$.
\end{enumerate}
\begin{assumption}[Strong DDH assumption]\label{ass:strong ddh}.  Let $n$ be a security parameter and let $p = 2q+1$ be a randomly chosen $n$-bit safe prime.  Consider the group $Q$ of quadratic residues in $\mathbb{F}_p^*$.  For any $W$ with $\Hoo(W)= \omega(\log n)$ where the domain of $W$ is $\mathbb{F}_q$, for $g\overset{\$}\leftarrow Q, a\leftarrow W, b,c \overset{\$}\leftarrow \mathbb{F}_q$, the ensembles $\langle g, g^a, g^b, g^{ab}\rangle$ and $\langle g, g^a, g^b, g^c\rangle$ are computationally indistinguishable.
\end{assumption}
\begin{theorem}~\cite{canetti1997towards}
The construction above, when instantiated with the group $G = Q$ is a virtual black-box obfuscator for the family of point functions under \assref{ass:strong ddh}.
\end{theorem}

As mentioned above there exist other constructions of point function obfuscation under various assumptions~\cite{lynn2004positive, wee2005obfuscating}.

Lastly, we will need the notion of composable obfuscation.

\begin{definition}[Composable obfuscation~\cite{bitansky2010strong, canetti2008obfuscating,lynn2004positive}]
\label{def:obf comp}
A PPT algorithm $\mathcal{O}$ is a $t$-\emph{composable obfuscator} for the family $\mathcal{C}$ with dependent auxiliary input if functionality and polynomial slowdown hold as before, and the virtual black black-box property holds whenever the adversary and simulator are given up to $t$ circuits in $\mathcal{C}$.  That is, for every PPT $A$ and polynomial $\rho$, there exists a PPT $S$ such that for all sufficiently large $n$, and for all $C_1,..., C_t\in \mathcal{C}_n$, and for all auxiliary inputs $z\in \zo^*$,
\[
|\Pr[A(\mathcal{O}(C_1), ..., \mathcal{O}(C_t), z) = 1] - \Pr[S^{C_1,..., C_t}(1^n, z) = 1]| < \frac{1}{\rho(n)},
\]
where the probabilities are taken over the random coins tosses of $A, S$ and $\mathcal{O}$.  The runtimes of $A$ and $S$ must be polynomial in the length of their first input.
\end{definition}

\section{Fuzzy Conductors}

@@

\section{$gap<0$ for Irises}
\label{sec:iris no key}
The iris is the biometric believed to have the most entropy.  The best estimate for iris entropy is $250$ bits~\cite{daugman2004}.  Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.  The transform computes a phase angle at $1024$ locations, this angle is then quantized into a positive/negative value in the two dimensions.  This transform is designed for the process of identification, achieving the best possible true accept/false accept tradeoff.

The precise number of errors that must be tolerated depends on the desired true accept rate (how often the correct key is produced).  For a true accept rate of $20\%$, a $t$ of approximately $205$ is required.\footnote{Daugman considerably improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.  The comparison between the two readings is then made using bits not excluded by either image.  It is not clear how to extend into the fuzzy extractor setting.}  We have the following calculation for $gap$:
\begin{align*}
gap &= \Hoo(W) - \log |B_t|\\
&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -707.
\end{align*}
Irises are believed to be the strongest biometric and reliable key derivation from irises is an open problem.

\section{Minimal Conditions for Fuzzy Extractor Security}
\label{sec:minimal conditions}
As mentioned in the introduction a necessary condition for fuzzy extractor security is that a negligible portion of the source distribution lies within any Hamming ball.  In the interactive setting using multi-party computation it is possible to achieve security under this condition.  We codify this notion:

\begin{definition}
\label{def:fuzzy min-ent}
A distribution $W$ in a metric space $\mathcal{M}$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) = k$ if the following holds:
\[
\forall m\in \mathcal{M} Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
\]
\end{definition}
\begin{lemma}
Let $n$ be a security parameter and let $W$ be a distribution over $\mathcal{M}$
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that corrects is secure against nonuniform adversaries of size $\log \mathcal{M} + |\rep|$ for negligible $\epsilon$~(and thus no fuzzy extractor) if $\kappa =\omega(\log n)$.
\end{lemma}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m\mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item On input $r, p$.
\item If $\rep(m, p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
First note that $|D|$ is of size $\log |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n)$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} - \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
\end{proof}

@@

\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent so a equality query on block $i$ may shape the distribution of block $j$.  Thus, we begin with the case of independent blocks.

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,..., W_\ell$ be a source where blocks are independent.  Let $\alpha$ be a parameter.  Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of blocks such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.  Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
\end{claim}
\begin{proof}
We ignore the blocks outside of $\mathcal{I}$ as queries on these blocks do not change the distribution of $W_i$ where $i\in \mathcal{I}$.  It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.
Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we ignore all other blocks as they are independent).
Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.
Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.  We assume a deterministic adversary~(we assume the best coins are in nonuniform advice).  The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.  There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.  If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.  These responses can be removed as the response is deterministic.  Let $A'$ represent the sequence with all duplicate queries removed.  This sequence has at most a single $1$.  Thus, the total number of possible responses is $q+1$~(including the duplicates does not change the number of possible responses).  Thus, we have the following,
\begin{align*}
\Hav(W_i | View(S)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
&=\Hav(W_i |A') \\
&=\Hoo(W_i) - \log |A'|\\
&=\alpha - \log |A'|\\
&=\alpha - \log (q+1)
\end{align*}
Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
This argument holds for all $i$.  This completes the proof.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} captures this type of distribution.

@@

\noindent Now by the security of obfuscation we have that
\begin{align}
\label{eq:dist after}
|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\leq \epsilon_{obf}.
\end{align}
Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish}, we have
\begin{align*}
\delta^{D}(( P, C), (P, C'))&\leq |\expe \expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)]| \\
&+|\expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C)] - \expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\\
&+|\expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] - \expe [D(P_1,..., P_\ell, C') ]|\\
&\leq \epsilon_{obf} + (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{obf}.
\end{align*}
This completes the proof of \thref{thm:security of cons}.
\end{proof}

>>>>

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}
\newcommand{\guess}{\mathsf{guess}}

@@

\subsection{Obfuscation}
Our construction uses obfuscation for a family of point function $\mathcal{I} = \{I_w\}_{w \in \zo^*}$ defined as follows:
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
\]
The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}. This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}) as it allows the simulator to run in unbounded time while making at most polynomial number of oracle queries to the function. In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input. Composable auxiliary-input VGB obfuscators for point functions are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.

\begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
\label{def:obf} Let $\mathcal{I}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is a $\ell$-composable VGB obfuscator for $\mathcal{I}$ with auxiliary-input if the following conditions are met:
\begin{enumerate}
\item \emph{Functionality:} for every $I \in \mathcal{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathcal{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
\[
|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^t)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
\]
where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
\end{enumerate}
\end{definition}

@@

\begin{definition}
\label{def:block guessable}
Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that returns \[\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=
\begin{cases}
1 & w_i = w_i'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} \lnote{is it ''block unguessable'' or ''unguessable block''? the usage is inconsistent}if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.
We discuss  block unguessable distributions in \apref{sec:characterize}.  \consref{cons:first construction} is secure for block unguessable distributions:
\begin{theorem}
\label{thm:security of cons}
Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\zo^n$. %that is $(s_{obf}, \epsilon_{obf})$-hard.  
Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq |C| - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{theorem}

@@

Combining the last two sections, we have that \consref{cons:sampling} is secure and correct:
\begin{theorem}
Let $n$ be a security parameter.
Let $\mathcal{W}$ be the family of $(\alpha = \omega(1), \beta\leq \gamma(1/2-\Theta(1)))$-unordered block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.  Let $\eta = \omega(\log n)$ and $\ell = O(\poly(n)) = \omega(\log n)$.  Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.  Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$-hard with error $\delta$ for
\begin{align*}
t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} \\
\tilde{m} &=|C|\\
\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
\end{align*}
\end{theorem}

\subsection{Discussion of \consref{cons:sampling}}
\consref{cons:sampling} achieves $H_{usable}<0$ for an interesting setting of parameters.  The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.  We are able to correct $O(\gamma/\eta)$ errors.
This yields:
\begin{align*}
H_{usable} &= \Hoo(W) -\log |B_t| \\
&< \Theta(\gamma)- t \log |\mathcal{Z}|\\
&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|
\end{align*}
That is, \consref{cons:sampling} achieves $H_{usable}<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.  If we are willing to accept $H_{usable}\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.  However, in this setting $H_{usable} =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
\bibliographystyle{alpha}
\bibliography{crypto}

\appendix
\section{Fuzzy Conductors}

@@

\section{Inadequacy of Fuzzy Extractors for Biometrics}
Fuzzy extractors were developed to derive stable from noisy sources.  Biometrics represent an important noisy physical source.  Unlike physical unclonable functions, biometrics are inherently fixed distributions.  It is not possible to increase their entropy or reduce their error to improve key strength.  Many biometric systems have incorporated fuzzy extractors to improve system security~(see the work of Jain, Nadakumar, and Nagar for a survey~\cite{jain2008biometric}).  The security of the resulting system is usually measured using false accept rate vs. false reject rate.  This assumes an adversary that creates inputs to the \rec algorithm without looking at the public helper data.  A known false accept rate provides there is no guarantee helper data information-leakage.  Indeed the helper data may completely reveal the original input.  In high security applications, this type of analysis is sufficient.

\label{sec:iris no key}
As an example, the iris is the biometric believed to have the most entropy.  The best estimate for iris entropy is $250$ bits~\cite{daugman2004}.  Daugman uses specialized wavelets to derive a $2048$ bit string called an iris code.  The transform computes a phase angle at $1024$ locations, this angle is then quantized into a positive/negative value in the two dimensions.\footnote{There is considerable subsequent research after the work of Daugman~\cite{daugman2004}.  These works do not dramatically improve the original results.}

The precise number of errors that must be tolerated depends on the desired false reject rate (how often the correct key is produced).  For a false reject rate of $\le 80\%$, a $t$ of approximately $205$ is required.\footnote{Daugman considerably improves his true accept rate using a masking vector, where bits that are not considered ``trustworthy'' are excluded from the comparison.  The comparison between the two readings is then made using bits not excluded by either image.  It is not clear how to extend into the fuzzy extractor setting.}  We have the following calculation for $H_{usable}$:
\begin{align*}
H_{usable} &= \Hoo(W) - \log |B_t|\\
&= 249 - \log \sum_{i=0}^{205} {2048 \choose i} = -707.
\end{align*}
Although irises are believed to be the strongest biometric a fuzzy extractor with the above parameters may completely reveal the original value.

%Fingerprints are in a similar situation.  Ratha, Connell, and Bolle estimate that fingerprints contain $82$ bits of entropy~\cite{ratha2003biometrics}.
%\bnote{Don't know what I want to say about fingerprints right now.  
\section{Minimal Conditions for Fuzzy Extractor Security}
\label{sec:minimal conditions}
A necessary condition for fuzzy extractor security is that a negligible portion of the source distribution lies within any Hamming ball.  We make this intuition formal here:

\begin{definition}
\label{def:fuzzy min-ent}
A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
\[
\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
\]
\end{definition}
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that corrects is secure against nonuniform adversaries of size $\log \mathcal{M} + |\rep|$ for negligible $\epsilon$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m\mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item On input $r, p$.
\item If $\rep(m, p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
First note that $|D|$ is of size $\log |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n)$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} - \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
\end{proof}

\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.  This means that fuzzy min-entropy is a necessary condition for an interactive solution as well.  The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.  When $H_{usable}<0$ there is some distribution such that $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution of all points within distance $t$).  This means we inherently must talk about the security and errors together.

@@

\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may shape the distribution of block $j$.  Thus, we begin with the case of independent blocks.

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\ell$ be a source in which all blocks $W_i$  are mutually independent.  Let $\alpha$ be a parameter.  Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
\end{claim}
\begin{proof}
It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) = \alpha -\log q$.
We can ignore queries for all blocks but the $i$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $\mathcal{A}$ \lnote{is the adversary $S$, $\mathcal{A}$, or $A$?} making $q$  queries about the $i$th block. Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
&=\Hoo(W_i) - H_0(A_1, \dots, A_q)\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} captures, in particular, this class of distributions.

@@

\noindent Now by the security of obfuscation we have that
\begin{align}
\label{eq:dist after}
|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\leq \epsilon_{sec}/3.
\end{align}
Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish}, we have
\begin{align*}
\delta^{D}(( P, C), (P, C'))&\leq |\expe \expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)]| \\
&+|\expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C)] - \expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\\
&+|\expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] - \expe [D(P_1,..., P_\ell, C') ]|\\
&\leq \epsilon_{sec}/3+ (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{sec}/3 \\
&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
\end{align*}
This is a contradiction and completes the proof of \thref{thm:security of cons}.
\end{proof}
